### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to times

At a time of 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes. As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW before it reached a steady-state value of approximately 20~MW. The predicted HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
\input{../Figures/colorbar_metric_pres}
\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
\input{../Figures/colorbar_metric_pres}
\caption[Simulated pressure contours on the right interior side of the structure.]
{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s). The fire originated in the living room in the basement.}
\label{fig:smv_pressure}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity contours on the right interior side of the structure.]
{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity vectors on the right interior side of the structure.]
{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the right interior side of the structure.]
{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature vectors on the right interior side of the structure.]
{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor before basement window failure.]
{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
\label{fig:smv_flow_path_top_1}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor after basement window failure.]
{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
\label{fig:smv_flow_path_top_2}
\end{figure}

>>>>

At 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes. As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW before it reached a steady-state value of approximately 20~MW. The predicted HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
\input{../Figures/colorbar_metric_pres}
\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
\input{../Figures/colorbar_metric_pres}
\caption[Simulated pressure contours on the right interior side of the structure.]
{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure. The fire originated in the living room in the basement.}
\label{fig:smv_pressure}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity contours on the right interior side of the structure.]
{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity vectors on the right interior side of the structure.]
{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the right interior side of the structure.]
{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature vectors on the right interior side of the structure.]
{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor before basement window failure.]
{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure.}
\label{fig:smv_flow_path_top_1}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor after basement window failure.]
{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
\label{fig:smv_flow_path_top_2}
\end{figure}
